### 2021-05-17 geography/ia/paper.tex
automatic wordcount for vscode. requires extension with id "emeraldwalk.runonsave"

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        Geography\\
        Internal Assessment \\
        \vspace{1cm}
        How does environmental quality, determined by the severity of pollution and the availability of green spaces, differ between a tourist-catering area of Paris versus a residential area? \\
        \vspace{1cm}
        \textit{Väinö-Verneri Kauppila} \\
        May 2021 \\
        \vspace{4cm}
        Word count: \textit{TBD} \\
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

\section{Introduction}

@@

\section{Method}

@@

This site was chosen as, like stated before, it is a residential area. There are other residential areas in Paris, however this one was specifically chosen for reasons of convenience.

@@

In order to either support or disprove our third hypothesis, it is important to study how trees are scattered in Paris, which reveals how dispersed green spaces are from one another. A statistical test called the Nearest Neighbor Index (NNI) test can provide a reasonable answer to this: if the index is similar for both sites, it can easily be said then that our hypothesis is supported. This value also reveals information about the distribution of trees: clustered, random or in a regular pattern, as seen in Figure 5 below.

@@

\section{Analysis}

@@

\section{Conclusion}

>>>>

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        Geography\\
        Internal Assessment \\
        \vspace{1cm}
        How does environmental quality, determined by the severity of pollution and the availability of green spaces, differ between a tourist-catering area of Paris versus a residential area? \\
        \vspace{1cm}
        \textit{Väinö-Verneri Kauppila} \\
        May 2021 \\
        \vspace{4cm}
        \input{wordcount.txt}
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

\section{Introduction}
\label{sec:intro}

@@

\section{Method}
\label{sec:method}

@@

This site was chosen as, like stated before, it is a residential area. There are other residential areas in Paris, however this one was specifically chosen for reasons of convenience.\footnote{We had 2 members of our group residing in this area.}

@@

In order to either support or disprove our third hypothesis, it is important to study how trees are scattered in Paris, which reveals how dispersed green spaces are from one another. A statistical test called the Nearest Neighbor Index (NNI) test can provide a reasonable answer to this: if the index is similar for both sites, it can easily be said then that our hypothesis is supported. This value also reveals information about the distribution of trees: clustered, random or in a regular pattern, as seen in Figure 5 below. These values will be analysed in the later section \ref{sec:analysis} Analysis.

@@

\section{Analysis}
\label{sec:analysis}

@@

\section{Conclusion}
\label{sec:conclusion}
